### 2022-07-22 paper/localpsf.tex
modify figures in paper
edit paper a small amount
have included the Stokes model description draft, included one more digit in the condition number table

Some numerical results here.

@@

\begin{figure}[H]
	\begin{subfigure}{0.59\textwidth}
	\begin{center}
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=0.8\linewidth,
		ymode=log,
		xmin=-50,
		xmax=1450,
		ymax=1.e4,
		xlabel={$k$, generalized eigenvalue \#},
		ylabel={$\lambda_{k}$},
		xtick={0, 300, 600, 900, 1200},
		%legend pos=north east,
		legend style={font=\small},
		ylabel near ticks, ylabel shift={-6pt},
		axis x line*=bottom,
		axis y line*=left,
		legend style={at={(0.95,1)},anchor=north east},
		title={Generalized eigenvalues, $Hu_{k}=\lambda_{k}Pu_{k}$}
		]
		\addlegendentry{PSF (1)}
        \addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues.dat};
        \addlegendentry{PSF (5)}
        \addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues.dat};
        \addlegendentry{PSF (25)}
        \addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues.dat};
		\addlegendentry{REG}
		\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues.dat};
		\end{axis}
		\end{tikzpicture}
	\end{center}
\end{subfigure}
\begin{subfigure}{0.39\textwidth}
		\begin{center}
		\begingroup
		\setlength{\tabcolsep}{4pt}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabular}{c| c c}
			& $\kappa(P^{-1}H)$ &	$\kappa(P^{-1}H_{\text{gn}})$ \\
			\hline 
			PSF $(1)$  & \verb~1.8e+1~ & \verb~1.8e+1~ \\
            PSF $(5)$  & \verb~1.4e+1~ & \verb~1.4e+1~ \\
            PSF $(25)$ & \verb~1.0e+1~ & \verb~1.1e+1~ \\
			REG        & \verb~7.0e+3~ & \verb~7.0e+3~ \\
			NONE       & \verb~8.7e+2~ & \verb~9.2e+2~ 
		\end{tabular}
		\endgroup
	\end{center}
\end{subfigure}
\end{figure}

>>>>

We next test the local psf framework on an inverse problem governed by a PDE which models steady-state ice sheet flow.
The domain that is covered by ice is denoted by
$\Omega\subset\mathbb{R}^{d}$, $d=3$,
$\Gamma_{b}$, $\Gamma_{l}$, and $\Gamma_{t}$ denote
the basal, lateral and top parts of the domain boundary
$\partial\Omega$.
The governing equations are the linear incompressible Stokes
equations,

\begin{subequations}\label{Stokeseqn}
	\begin{align}
	-\nabla\cdot\bm{\sigma}_{\bm{u}}
	&=\rho\bm{g}\,\,\,\text{ in }\Omega, \label{Stokeseqn:1}\\
	\nabla\cdot\bm{u}
	&=0\,\,\,\,\,\,\text{ in }\Omega, \label{Stokeseqn:2}\\
	\bm{\sigma}_{\bm{u}}\bm{n}
	&=\bm{0}\,\,\,\,\,\,\text{ on }\Gamma_{t}, \label{Stokeseqn:3}\\
	\bm{u}\cdot\bm{n} =0 \text{ and } \bm{T}\left(\bm{\sigma}_{\bm{u}}\bm{n}+\exp\left(m\right)\bm{u}\right)
	&=\bm{0}\,\,\,\,\,\,\text{ on }\Gamma_{b},\label{Stokeseqn:4} \\
	\left(\bm{\sigma}_{\bm{u}}\bm{n}+\mu\bm{u}\right)&=\bm{0}\,\,\,\,\,\,\text{ on }\Gamma_{l},\label{Stokeseqn:5}	
	\end{align}
\end{subequations}
whose solution determines the ice flow velocity $\bm{u}$ and pressure $p$. Here, $m$ is the logarithmic
basal sliding parameter field, $\rho\bm{g}$ the body force density due to gravity, $\bm{n}$ is the outward normal and $\bm{T}$ is a tangential projection operator. 
We employ Glen's flow law
(CITE GLEN) %\cite{glen1955},
which is a constitutive law for ice that relates the stress
tensor $\bm{\sigma}_{\bm{u}}$ and the strain rate tensor
$\bm{\dot{\varepsilon}}_{\bm{u}}= \frac{1}{2}\left(
\bm{\nabla}\bm{u}+\bm{\nabla}\bm{u}^{\top} \right)$, $\bm{\sigma}_{\bm{u}}= 2\eta
\bm{\dot{\varepsilon}}_{\bm{u}} -\bm{I}p$, where $\eta=\frac{1}{2}A^{-1}$ is the effective viscosity, $\bm{I}$ is the unit matrix,
and $A$ is a flow rate factor. Glen's exponent has been chosen $n=1$, which provides for a linear Stokes model.

@@

\begin{figure}[H]
	\begin{subfigure}{0.59\textwidth}
	\begin{center}
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=0.8\linewidth,
		ymode=log,
		xmin=-50,
		xmax=1450,
		ymax=1.e4,
		xlabel={$k$, generalized eigenvalue \#},
		ylabel={$\lambda_{k}$},
		xtick={0, 300, 600, 900, 1200},
		%legend pos=north east,
		legend style={font=\small},
		ylabel near ticks, ylabel shift={-6pt},
		axis x line*=bottom,
		axis y line*=left,
		legend style={at={(0.95,1)},anchor=north east},
		title={Generalized eigenvalues, $Hu_{k}=\lambda_{k}Pu_{k}$}
		]
		\addlegendentry{PSF (1)}
        \addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues.dat};
        \addlegendentry{PSF (5)}
        \addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues.dat};
        \addlegendentry{PSF (25)}
        \addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues.dat};
		\addlegendentry{REG}
		\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues.dat};
		\end{axis}
		\end{tikzpicture}
	\end{center}
\end{subfigure}
\begin{subfigure}{0.39\textwidth}
		\begin{center}
		\begingroup
		\setlength{\tabcolsep}{4pt}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabular}{c| c c}
			& $\kappa(P^{-1}H)$ &	$\kappa(P^{-1}H_{\text{gn}})$ \\
			\hline 
			PSF $(1)$  & \verb~1.75e+1~ & \verb~1.76e+1~ \\
            PSF $(5)$  & \verb~1.39e+1~ & \verb~1.39e+1~ \\
            PSF $(25)$ & \verb~1.03e+1~ & \verb~1.06e+1~ \\
			REG        & \verb~7.02e+3~ & \verb~7.02e+3~ \\
			NONE       & \verb~8.71e+2~ & \verb~9.22e+2~ 
		\end{tabular}
		\endgroup
	\end{center}
\end{subfigure}
\end{figure}
